Generating Correlated Data for Omics Simulation

### 2025-06-02 manuscript/supplemental/supplemental.qmd
Incorporate metabolomics dataset

>>>>

```{r}
#| label: fig-compare-to-real3
#| fig-cap: "Comparison to plasma metabolomics data set, obtained from MetaboAnalyst (https://www.metaboanalyst.ca/MetaboAnalyst/upload/RocUploadView.xhtml). Methods were run using normal marginal distributions. Unlike other examples, this included more samples (59) than measured features (42 metabolites), demonstrating that these methods also work in that case."
#| fig-width: 10
#| fig-height: 10
readRDS("../../processed/compare_to_real_plot_metabolomics.RDS")
```
